Supplementary Information

### 2021-08-10 doc/manuscript/response_to_reviews.Rmd

---
title: ''
output: 
    word_document
bibliography: references.bib
csl: global-change-biology.csl

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dear Editor:

We are pleased to submit a revised version of our manuscript, "Joint effects of climate, tree size, and year on annual tree growth derived from tree-ring records of ten globally distributed forests" (GCB-21-1209, for consideration for publication in *Global Change Biology*. We have addressed all points raised by the reviewers, as detailed below. The most significant changes include:

@@

L302-303: DBH interactions with climate? Or climate-climate interactions?

**We have clarified this: "..DBH (included in models with DBH and DBH-climate interactions)."**

P20-21: Various recent publications have highlighted the importance of the effect of climate interactions and climate disturbance interactions on tree growth. It is not clear to me why the DBH-climate interactions were included, but climate-climate interactions were not.

**Our method could be used to examine climate-climate interactions, and we believe that would be a valuable thing to do; however, we did not include that here because (1) the scope of the analysis is already very large and challenging to present concisely, and (2) we have limited time and resources to try all of the potentially interesting analyses. We now clarify this in the text: "We did not run models of precipitation $\times$ temperature, climate $\times$ DBH + year, or climate $\times$ year, which would be possible in the GLS model framework but would require additional statistical and conceptual validation beyond the scope of the current analysis."**

@@

L313: From what I understand, a concave up fit is perfectly reasonable. For example, a standard exponential growth function is concave up, and is biologically possible. Clarify. Also clarify on how they were excluded.

**Because the growth variable is log-transformed in our analysis, an exponential (concave-up) fit would be captured by a linear function. What we seek to exclude is u-shaped responses, which would not make sense biologically. We have clarified this in the text: "For climate response, we allowed concave-down fits, but ignored any concave-up fits on the basis that exponential functions would be captured by a linear fit to the log-transformed growth variables, while u-shaped fits are not expected biologically."**

L336-337: Is it also true that climate + DBH + climate x DBH + year is included? If not clarify why not.

**Our method could be used to do this, and we believe that would be a valuable thing to do; however, we did not include that here because (1) the scope of the analysis is already very large and challenging to present concisely, and (2) we have limited time and resources to try all of the potentially interesting analyses. We now clarify this in the text: "We did not run models of precipitation $\times$ temperature, climate $\times$ DBH + year, or climate $\times$ year, which would be possible in the GLS model framework but would require additional statistical and conceptual validation beyond the scope of the current analysis."**

### 2021-08-11 doc/manuscript/ForestGEO_treerings.Rmd
added sentence on analyses not run
Update ForestGEO_treerings.Rmd
#136

Within each of three categories of models run (climate only, climate + DBH, climate $\times$ DBH, climate + DBH + year), we selected as the top model that with the lowest AIC.

@@

```{r , eval=FALSE, echo=FALSE}
# This draw.io diagram that can be edited online here: https://app.diagrams.net/#HEcoClimLab%2FForestGEO-tree-rings%2Fmaster%2Fdoc%2Fmanuscript%2Ftables_figures%2FSummaryFigure.drawio
```
![**Figure 3 | Summary of top models for ring width (RW) as a function of climate (water and temperature variables), DBH, and calendar year**. Arrows approximate reponses detailed in Figs. 3, 5, and S16. Each symbol indicates one species, and species are ordered alphabetically within each site. Overlapping solid and dotted arrows for the same species indicate that the effect changed when *Year* was included in the model, with dotted arrows indicating the response without *Year*. Interactive effects of climate and DBH are not shown.](tables_figures/SummaryFigure.png)

>>>>

Within each of three categories of models run (climate only, climate + DBH, climate $\times$ DBH, climate + DBH + year), we selected as the top model that with the lowest AIC. 
We did not run models of precipitation $\times$ temperature, climate $\times$ DBH + year, or climate $\times$ year, which would be possible in the GLS model framework but would require additional statistical and conceptual validation beyond the scope of the current analysis.

@@

```{r , eval=FALSE, echo=FALSE}
# This draw.io diagram that can be edited online here: https://app.diagrams.net/#HEcoClimLab%2FForestGEO-tree-rings%2Fmaster%2Fdoc%2Fmanuscript%2Ftables_figures%2FSummaryFigure.drawio
```
![**Figure 3 | Summary of top models for ring width (RW) as a function of climate (water and temperature variables), DBH, and calendar year**. Arrow shapes approximate reponses detailed in Figs. 3, 5, and S16. Each symbol indicates one species, and species are ordered alphabetically within each site. Overlapping solid and dotted arrows for the same species indicate that the effect changed when *Year* was included in the model, with dotted arrows indicating the response without *Year*. Interactive effects of climate and DBH are not shown.](tables_figures/SummaryFigure.png)
